Probability

### 2016-04-14 prob.tex
[4] JM Swart. Introduction to quantum probability. Lecture Notes, 2013.

As an example, let $P_1, P_2, \ldots, P_k$ be mutually orthogonal
projections on $\Hilb$ with sum $\mathbbm{1}$ and define the event
space $\qevents$ to be the linear span of these operators:
\[
\qevents = \{ \sum_{j=1}^k \lambda_jP_j ~|~ \lambda_i, \ldots, \lambda_k \in \mathbb{C} \}. 
\]
Each state $\psi$ of the Hilbert space induces a probability measure
$\phi_\psi : \qevents \rightarrow [0,1]$ defined as follows:
\[
\phi_\psi(A) = \langle \psi ~|~ A\psi \rangle
\]

>>>>

As an example, let $P_1, P_2, \ldots, P_k$ be mutually orthogonal
projections on $\Hilb$ with sum $\mathbbm{1}$ and define the event
space $\qevents$ to be the linear span of these operators:
\[
\qevents = \{ \sum_{j=1}^k \lambda_jP_j ~|~ \lambda_i, \ldots, \lambda_k \in \mathbb{C} \}. 
\]
\yutsung{If we want to follow Swart~\cite{Swart2013}... Maybe we
should define the set of projection and the }\\
Each state $\psi$ of the Hilbert space induces a probability measure
$\phi_\psi : \qevents \rightarrow [0,1]$ defined as follows:
\[
\phi_\psi(A) = \langle \psi ~|~ A\psi \rangle
\]
